### 2013-06-07 Rcode/intro.rmd
added ability to specify sigmaavec

beta.ash=ash(ss$betahat,ss$betasd)
#compute the usual zscore and corresponding p value
zscore = ss$betahat/ss$betasd
pval = pchisq(zscore^2,df=1,lower.tail=F)
qval = qvalue(pval)
```

>>>>

beta.ash=ash(ss$betahat,ss$betasd)
#compute the usual zscore and corresponding p value
zscore = ss$betahat/ss$betasd

pval = pchisq(zscore^2,df=1,lower.tail=F)
qval = qvalue(pval)
hist(zscore)
```
